---
title: "general replacement script"
author: "Kate Sheridan"
date: "8/30/2022"
output: html_document
---

This is a general script for using the keys with eDNA data.
Paste the relevant chunks into your QC script.

THIS CODE WILL NOT WORK AS IS! Replace all filepaths and filenames with your own.


# Setup

Add any relevant portions to your own setup chunk.

```{r setup, include=FALSE}
# not necessary if you already have tidyverse loaded
library(dplyr)
library(readr)


library(here)
# update this filepath to your own keys
## separate subdirectories with a comma
keys <- here("latest-keys")
ednadata <- here("filepath_to", "edna_data")
specieslist <- here("filepath_to", "species_lists")
```

# Load in

Note that the object names are generic. If you're using multiple markers in the script, update the names to be unique

```{r loadin}
#eDNA taxonomy table;
## this should contain a list of ASVs matched to IDs
taxonomy_edna <- read.delim(here::here(ednadata, 'taxonomy_table_file.txt'), 
                           h = TRUE, fill = TRUE) %>% 
  janitor::clean_names()

# often the taxonomy tables give us odd column names; remove the hanging x_ if necessary
colnames(taxonomy_edna) <- taxonomy_edna %>%
  colnames(.) %>% 
  str_remove_all(string = .,
                 pattern = "x_")


# Latest key
taxa_key <- read_csv(here(specieslist,
                     'date_marker_rosetta_draft.csv'))



# Known Replacements if applicable
taxa_replace <- read_csv(here(specieslist,
                     'date_marker_replacements.csv')) %>%
  # remove any incomplete rows; lists still in progress
  filter(!(is.na(new_id))) %>%
  # other columns not needed at the moment; still improving spreadsheets!
  select(species_old, new_id, id_note)


```

# Clean eDNA results

Note that the column of eDNA IDs is called lca taxon; this may not be your column name.

## for 12s

```{r}
# for mifish we only want fish
## this should give a list of only asv# + ID
taxonomy_edna <- taxonomy_edna %>%
  #filter(phylum == "Chordata") %>% # this could also give us whales if we want
  ## class is more efficient for our needs
  # be careful with bony fish:might be written different ways
  filter(class %in% c('Chondrichthyes', 'Actinopteri')) %>% 
  # here filter to generic or below
  filter(lca_rank %in% c('genus', 'species', 'subspecies')) %>%
  #then strip only species column
  select(query, lca_taxon) %>%
  rename(asv = query)


# replace from list if applicable
# this will output ASV, taxon replaced, new taxon, and note from sheet
# the output is ONLY ASVs that were based on ONLY taxonomy
## NOTE currently the sheet is for BC-ONLY replacements
## NOTE this may drop some species to genus.
mifish_replacement <- taxonomy_edna %>%
  filter(lca_taxon %in% taxa_replace$species_old) %>%
  left_join(taxa_replace, by = c('lca_taxon' = 'species_old')) %>%
  rename(lca_taxon_replaced = lca_taxon,
         lca_taxon = new_id)


taxonomy_edna2 <- taxonomy_edna %>%
  # replacements back into list
  filter(!(lca_taxon %in% mifish_replacement$lca_taxon_replaced)) %>%
  bind_rows(mifish_replacement) %>%
  # match
  left_join(taxa_key, by = c('lca_taxon' = 'species_verbatim')) %>%
  # you may not need all the columns, these are the most useful
  ## FOUND_TAXA is your new ID
  select(asv, found_taxa, taxa_query, lca_taxon, rank,
         phylum, class, order, family, genus,
         freshwater_only, terrestrial_only, status, unacceptreason,
         worms_aphiaid, bold_id, gbif_key, ott_id,
         lca_taxon_replaced, id_note) %>%
  distinct() 


# sort out not matched; key needs to be updated for these taxa
not_matched <- taxonomy12s_2 %>%
  filter(is.na(found_taxa)) %>%
  select(asv, lca_taxon)


# write out final taxonomy
write.csv(taxonomy_edna2, here(ednadata, 'date_marker_taxonomy.csv'))

```



## for COI



```{r}
# filter out non-marine invertebrates
taxonomy_edna <- taxonomy_edna %>%
  # sometimes kingdom == 'Animalia' depending on table
  filter(kingdom == 'Eukaryota') %>%
  # remove not-desired phylum (You may need to add more Protists/etc for your dataset)
  filter(!(phylum %in% c('Bacillariophyta', 'Haptista', 'Rhodophyta', 
                         'unknown phylum', 'no identification'))) %>%
  # remove fish, birds, mammals, etc, separately to retain tunicates, etc
  ## marine inverts that may be classed as 'chordata'
  filter(!(class %in% c('Chondrichthyes', 'Actinopteri', 'Mammalia', 
                        'Aves', 'Amphibia'))) %>%
  # filter for below-genus
  filter(lca_rank %in% c('genus', 'species', 'subspecies')) %>%
  # only retain relevant columns; higher taxonomy will be reassigned
  select(query, lca_taxon)
```





# Filtering updated taxonomy

Now you can use freshwater/terrestrial columns and problem keys to filter if needed

```{r fresh-terrestrial}



```

For problem keys, either load the whole key or only the relevant problem
These are under construction as the species on them are researched and eventually added to the replacement key
For many of them, it may be advisable to just step back to genus.

```{r problem-key}
# finally check if any of the species are in the problem key
problem_key <- read_csv(here(specieslist,
                     '20220118_remove_from_splists_fish.csv')) %>%
  # optional; only load in columns and values you want to filter by
  select(species, not_nearshore, other_problem) %>%
  filter(not_nearshore == 1 | other_problem == 1)

#identify ASVs that may be a problem
## this includes not-matched, species on the problem key, and freshwater/terrestrial only
edna_problems <- taxonomy_edna2 %>%
  filter(found_taxa %in% problem_key$species | is.na(found_taxa) | freshwater_only == 1 | terrestrial_only == 1)

```

