---
title: "12sMifish_03_intermediate-update"
output: html_document
date: "2022-08-02"
---

```{r setup, include=FALSE}
library(tidyverse)
library(stringr)
library(taxize)
library(here)

# here filepaths
# here filepaths
problems <- here('species_lists', 'hakai', '2022rosetta', 'problems')
```

```{r worms-function}
library(worrms)

## requires worrms to be loaded
# input is vector of species names
# use wm_records_names to extract 
# this doesn't need the + signs

# right now this breaks if not-found
search_records_worms <- function(spnames) {
  search <- tibble()
  for (i in spnames) {
    print(paste0('searching for ', i))
    record <- wm_records_names(i, marine_only = FALSE)
    message('done')
    search <- append(search, record)
  }
  names(search) <- spnames
  search_output <- map_dfr(.x = search, ~ data.frame(.x), .id = 'query') %>%
    janitor::clean_names() %>%
    select(!(c(url, taxon_rank_id, citation, lsid, modified)))
  return(search_output)
}
```



# Not matched

These were not matched when rosetta was deployed to an actual project. May reflect an updated database from Hakai, but for here we'll fix them manually or identify why they weren't matched; possibly a problem above.

Here we will use the existing rosetta to generate entries at the species or generic level, then any that are still not found we'll check that they aren't on the problems lists.
```{r what needs matched?}
# load in current version

mifish_rosetta <- read_csv(here('latest-keys',
                                 '20220803_mifish_fish-only_rosetta_draft.csv'))#[-1]

# load in not matched list
not_matched <- read_csv(here(problems, 'other', '20220714_mifish-notmatched.csv'))

# load in replacements list
## often these are higher taxa that aren't found yet
mifish_replace <- read_csv(here('latest-keys', 'in_process_spreadsheets',
                                '20220802_mifish_replacements.csv')) %>%
  select(new_id) %>%
  rename(taxa_query = new_id) %>%
  distinct()

# if current version has not matched rows:
# filter them out, combine with not_matched
## this is not really an issue with mifish

# combine lists
not_matched <- not_matched %>%
  bind_rows(mifish_replace) %>%
  distinct()


table(mifish_rosetta$class)
```


```{r resolve-unmatched}
nm_resolved <- tol_resolve(not_matched$taxa_query)

nm_search <- nm_resolved %>%
  select(unique_name, search_string, ott_id, is_synonym, flags) %>%
  mutate(search_string = str_to_sentence(search_string)) %>%
  # remove any tol strings
  mutate(unique_name = str_remove_all(unique_name, ' \\(genus in Holozoa\\)')) %>%
  ## temporary issue requires replacing whitespace with '+'
  mutate(worms_query = gsub(" ", "+", unique_name)) %>%
  rename(tol_sciname = unique_name,
         identification = search_string)

nm_worms <- get_wormsid_(nm_search$worms_query, accepted = FALSE, marine_only = FALSE)
# unpack
nm_worms2 <- nm_worms %>% 
  compact() %>%
  discard( ~ nrow(.x) == 0) %>%
  map_dfr( ~ data.frame(.x), .id = 'worms_query')


# this cleaning step is relatively temporary until they fix the curl issue
nm_worms2 <- nm_worms2 %>%
  left_join(nm_search) %>%
  select(!(worms_query)) %>%
  # remove higher taxonomy with species-level hits
  filter(!(str_detect(tol_sciname, " ") == FALSE & str_detect(scientificname, " ") == TRUE)) %>%
  filter(!(!(tol_sciname == scientificname))) %>%
  select(!(c(status))) %>%
  rename(worms_aphiaid = AphiaID,
        worms_sciname = scientificname) %>%
  distinct()

# extract higher and info about freshwater
nm_records <- search_records_worms(nm_worms2$worms_sciname)

# refine results to be useful
nm_records <- nm_records %>%
  # only animal hits
  filter(kingdom == 'Animalia') %>%
  # generate terrestrial-only and freshwater-only columns
  mutate(freshwater_only = ifelse((is_marine %in% c(0, NA) ==TRUE) & (is_brackish %in% c(0,NA) == TRUE) & (is_freshwater == 1),  "1", "0")) %>%
    mutate(terrestrial_only = ifelse((is_marine %in% c(0, NA) ==TRUE) & (is_brackish %in% c(0,NA) == TRUE) & (is_terrestrial == 1),  "1", "0")) %>%
  distinct() %>%
  # rename to format
  rename(tol_sciname = query,
         worms_aphiaid = valid_aphia_id,
         original_aphiaid =aphia_id,
         worms_match = scientificname,
         worms_sciname = valid_name
         ) %>%
  # remove unneeded columns
  select(!(c(authority, parent_name_usage_id, is_freshwater, 
             is_terrestrial, is_marine, is_brackish, is_extinct, match_type))) %>%
  relocate(c(worms_sciname, worms_aphiaid), .before = original_aphiaid) %>%
  # rank lowercase
  mutate(rank = tolower(rank))

# run found thorugh the rest of the process

#3: gbif+bold ids
# now we'll search bold
nm_bold <- get_boldid_(sci = nm_search$tol_sciname, 
                         includeTree = TRUE,
                         divison = 'Animalia')
#bind up lists into a dataframe
nm_bold2 <- map_dfr(.x= nm_bold, ~ data.frame(.x)) %>%
  filter(!(is.na(input))) %>%
  filter(!(is.na(taxid))) %>%
  filter(tax_division == 'Animalia') %>%
  # remove cases where input is higher taxonomy and taxon is species epthet
  filter(!(str_detect(input, " ") == FALSE & str_detect(taxon, " ") == TRUE)) %>%
  select(!(c(representitive_image.image, 
             representitive_image.apectratio))) %>%
  remove_rownames() %>%
  relocate(input) %>%
  distinct() %>%
  # prep to merge with other searches
  rename(bold_id = taxid,
         tol_sciname = input,
         rank = tax_rank,
         bold_taxon = taxon) %>%
  select((c(tol_sciname, bold_id, bold_taxon, rank)))

# GBIF id
nm_gbifid <- get_gbifid_(sci = nm_search$tol_sciname, rows = 1)

nm_gbifid2 <- map_dfr(.x= nm_gbifid, ~ data.frame(.x), .id = 'tol_sciname') %>%
  filter(kingdom == "Animalia") %>%
  # eliminating fuzzy matches for now
  filter(matchtype == 'EXACT') %>%
  # strip higher taxonomy from gbif bc it doesn't match worms/bold
  ## but keep keys!
  select(!(c(kingdom, phylum, class, order, family, genus, species,
             status, confidence, canonicalname, matchtype, kingdomkey,
             # just keeping regular gbif key
             acceptedusagekey, phylumkey, orderkey,
             classkey, familykey, genuskey, specieskey,
             synonym, note))) %>%
    rename(gbif_key = usagekey,
         gbif_sciname = scientificname)



#4: merge all and find problems
# join all updated fields
to_match2 <- nm_search %>%
  left_join(nm_records) %>%
  left_join(nm_bold2) %>%
  left_join(nm_gbifid2) %>%
  relocate(c('worms_aphiaid', 'bold_id', 'gbif_key', 'ott_id'), .before = 'phylum') %>%
  relocate(c('worms_sciname', 'tol_sciname', 'bold_taxon', 'gbif_sciname'), .before = 'phylum') %>%
  #single column for TOL and WORMS replacements; bold and gbif tend to follow TOL
  mutate(found_taxa = coalesce(worms_sciname, tol_sciname)) %>%
  relocate(c('found_taxa', 'rank'), .before = 'worms_aphiaid') %>%
  relocate('family', .before = 'genus') %>%
  relocate(c('is_synonym', 'flags'), .before = 'valid_authority') %>%
  select(!(c(worms_query, worms_match, original_aphiaid))) %>%
  distinct() %>%
  mutate(freshwater_only = as.numeric(freshwater_only)) %>%
  mutate(terrestrial_only = as.numeric(terrestrial_only)) %>%
  select(!(kingdom)) %>%
  rename(species_verbatim = identification)
  
```



```{r bind and write}
mifish_rosetta <- mifish_rosetta %>%
  bind_rows(to_match2) %>%
  mutate(species_verbatim = coalesce(species_verbatim, taxa_query)) %>%
  # just in case anything snuck in thorugh fuzzy search
  filter(phylum == 'Chordata')


# write in update!
write_csv(mifish_rosetta, here('latest-keys',
                              '20220803_mifish_fish-only_rosetta_draft.csv'))

```






August 2022 touch up

last time I updated the key there was an issue; next time I need to check closely to find the error in the code.
New entries were added for some species, and didn't get a taxa_query
These entries are more complete than the originals so i should keep them and delete the old ones; and get found taxa populated
Problem is; its only keeping the first one with distinct() so we're losing the extra info. Figure this out later; it looks like the gbif column is empty generally so it might just be that the whole thing needs run for gbif again.

```{r}
library(dplyr)

mifish_rosetta2 <- mifish_rosetta %>%
  mutate(taxa_query = ifelse(is.na(taxa_query) == TRUE, found_taxa, taxa_query)) %>%
  distinct(species_verbatim, .keep_all = TRUE)
  
write_csv(mifish_rosetta2, here('latest-keys',
                              '20220831_mifish_fish-only_rosetta_draft.csv'))

```


