---
title: "12sMifish_01b_NCBI"
author: "Kate Sheridan"
date: "11/7/2022"
output: html_document
---
This uses the NCBI list from search: 12S (all fields), and fish taxonomy in organism field.
This will include only fish, and only sequences that have been annotated with 12S somewhere.
The csv loaded in has been manipulated with Python from the raw output to be a CSV. There is still mess in the species field, but that won't matter here.

NCBI does have taxonomy built in, but we want the output to match the COI output, and especially WoRMS taxonomy. Assumedly, there will be a lot here with only OTT codes as many of the fish will be freshwater.



```{r setup, include=FALSE}
library(tidyverse)
library(stringr)
library(taxize)
library(worrms)
library(here)

# here filepaths
hakai_blast <- here('species_lists', 'hakai')
rosetta <- here('species_lists', 'hakai', '2022rosetta')
```

```{r load-in}
# ncbi extract: 12S and fish
ncbi_fish <- read_csv(here(hakai_blast, '2022_ncbi', '20221102_ncbi_fish_rough.csv'), 
                      col_names = FALSE) %>%
  rename(species = X1,
         ncbi_id = X2)

```


```{r worms-function}
## requires worrms to be loaded
# input is vector of species names
# use wm_records_names to extract 
# this doesn't need the + signs

# right now this breaks if not-found
search_records_worms <- function(spnames) {
  search <- tibble()
  for (i in spnames) {
    print(paste0('searching for ', i))
    record <- wm_records_names(i, marine_only = FALSE)
    message('done')
    search <- append(search, record)
  }
  names(search) <- spnames
  search_output <- map_dfr(.x = search, ~ data.frame(.x), .id = 'query') %>%
    janitor::clean_names() %>%
    select(!(c(url, taxon_rank_id, citation, lsid, modified)))
  return(search_output)
}
```


NCBI ; UID
```{r ncbi classification}
fish_ncbi_tax <- genbank2uid(ncbi_fish$ncbi_id, db = 'ncbi')

fish_ncbi_tax2 <- fish_ncbi_tax %>% 
  compact() %>%
  #discard( ~ nrow(.x) == 0) %>%
  map_dfr( ~ data.frame(.x), .id = 'query')

fish_ncbi_query <- fish_ncbi_tax2 %>%
  select(ids) %>%
  distinct()

fish_ncbi_query1 <- fish_ncbi_query[1:3000,] %>% enframe()
fish_ncbi_query2 <- fish_ncbi_query[3001:6000,] %>% enframe()
fish_ncbi_query3 <- fish_ncbi_query[6001:9000,] %>% enframe()
fish_ncbi_query4 <- fish_ncbi_query[9001:12739,] %>% enframe()

# trying the whole set gave me 400 issues
#fish_ncbi_query4 <- fish_ncbi_query[1:12739,] %>% enframe()


fish_ncbi_classify <- classification(fish_ncbi_query4$value, db = 'ncbi')

fish_ncbi_classify2 <- map_dfr(.x= fish_ncbi_classify, ~ data.frame(.x), 
                                   .id = 'taxa_query') %>%
  distinct() %>%
  pivot_wider(names_from = rank, values_from = name, id_cols = taxa_query) #%>%
  #mutate(rank = 'species')

```

```{r merge and clean ncbi}
# set up and merge
# separate chunk for now to prevent accidents

# 1-5000
classify1 <- fish_ncbi_classify2
# 5001 - 10000
classify2 <- fish_ncbi_classify2
# 10001 - 12000
classify3 <- fish_ncbi_classify2
# 10001 - 12000
classify4 <- fish_ncbi_classify2

fish_ncbi_result <- bind_rows(classify1, classify2, classify3, classify4)

# clean results
# this will give us only the species and UID number, with the species cleaned as much as possible.
fish_ncbi_result <- fish_ncbi_result %>%
  # still extracting family and genus here for some troubleshooting
  select(taxa_query, family, genus, species, subspecies) %>%
  # columns are coming out as list columns, flatten
  unnest(cols = c(family, genus, species, subspecies)) %>%
  # replace null with na
  mutate(across(.cols = everything(), ~str_replace_all(., 'NULL', NA_character_))) %>%
  # subspecies will be the 'correct' id for some of these
  ## we will need to clean this column later; add at this point in script
  ## A lot of the things I removed in the original taxize script are embedded in the species names again
  ## so fix later, lets get the script moving to the next stage for now
  mutate(ncbi_sp = coalesce(subspecies, species)) %>%
  select(taxa_query, ncbi_sp) %>%
  #mutate(original_sp = ncbi_sp) %>%
  rename(species = ncbi_sp) %>%
  # remove brackets and special characters
  mutate(species = str_remove_all(species, "\\[|\\]|\\(|\\)|\\'|#|/|>|&|-|:|,|_")) %>%
   # remove 'sp'
  mutate(species = trimws(species)) %>%
    # species
  mutate(species = str_remove_all(species, "(sp\\. )|(sp\\.)$|( sp)$|(_sp_)|( sp[0-9])")) %>%
  # genus
  mutate(species = str_remove_all(species, "( Gen)|( gen n)|( gen)$|( gen\\. )|( gen )|( fam\\.)")) %>%
  # species complexes
  mutate(species = str_remove_all(species, "(cf\\. )|( cf)|( aff\\.)|^(aff\\. )|( species complex)|( Group )|( group )|( group)$|( gr\\.)|( complex)$|( complex )|( complex type)|( complexnew)|( complexc)|( var\\.)|( Var)$|( clade [A-Z]{1} )|( clade[0-9]{1})|( clade )|( clade)$|( nr\\.)|( unid\\.)|( und)$|( undet)$|( und_[0-9]{1})$|( unk)$|( unk_[0-9]{1})$| unnamed| sensu lato|  sesu lato|  sensu stricto|( intermediate )")) %>%
  mutate(species = trimws(species)) %>%
  # other taxonomy modifier
  mutate(species = str_remove_all(species, "( type )|(type[0-9]{2})|(type[0-9]{1})|( type)$|( n\\.)|( n )|( new)$|( nov\\.)|( nov )|(nomen nudum)")) %>%
  mutate(species = str_remove_all(species, " genotype| ecotype| morphotype| voucher| specimen| popvariant| museum|( et al)|( et al\\.)| field number|( sensu)| lineage| hybrid|( wild)|( var)$|(Natural )|( breed)|(mutant)$")) %>%
  # other meta-descriptors
  mutate(species = str_remove_all(species, "( collection)|( library)| Library| containing|( domain of)|( major)$|(_sample_)")) %>%
  # ways to say "fish"
  mutate(species = str_remove_all(species, "( efish)$|(eFish)$|(Fish)$|(Fisk)$|(Ichthyology)|(Ich)$|(IDEAFish)")) %>%
  # remove all numbers
  mutate(species = str_remove_all(species, "[0-9]")) %>%
  mutate(species = str_remove_all(species, "\\.")) %>%
  mutate(species = trimws(species)) %>%
  #remove the last character if its a capital letter many times
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  # in case multiple 'words'
  mutate(species = trimws(species)) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_remove_all(species, "mitochondrial|mitochondria|mitochodrial|mitochondral| cytochrome| oxidase| subunit|(cytb)| intergenetic| spacer| region| dehydrogenase| ribosomal| molecule| Clonal|( DNA No)")) %>%
  # Methods
  mutate(species = str_remove_all(species, "( Miseq)| RNAThr|(Zap Express)|( Photo)$| environmental sample")) %>%
  # morphology
  mutate(species = str_remove_all(species, "( spot)|( spot)|( barred)|( dwarf)|( large )|( small )| Cribrimorphlike|( pinnules)|( crescent)$|( spiral)$|(collar)|( Laser)|( Super)$|( special)$|( Illuminator)|( Long )|( Last)")) %>%
  mutate(species = str_remove_all(species, "( Head kidney)|(bulky head)|( brain)|( muscle)|( Tissue)|(Spleen of)|(gynotic )| infected|(prey of)|( larva)|( eyes)$| nudepalp|(palp)$|(Fin)$")) %>%
  # color
  mutate(species = str_remove_all(species, "( Black)| black| chocolate|( Green)|( green)|( Red)|( red )|( rosy)|(Verde)$| orangecollar| Orange|( yellow)|( Yellow)|( yellowback)|( yellowcollar)|( yellowpatch)|( Gold)|( albino )|( white)|( White)| blond")) %>%
  # other animal names
  mutate(species = str_remove_all(species, "( Tuna)|( Perche)|( blackcarp)|( carp gudgeon)|( Eel)|( Salmon)|(Mackerel)| Puma Loach|( Porcupine)| sawfin shiner| brassy jumprock|( chimpanzeecA)|( gibbongA)|( ex Sooretamys angouya)$|( Phantom)|(barbel steed)")) %>%
  # location modifiers
  mutate(species = str_remove_all(species, "(Lake )|( Lake)|( cave)$|( spring)$|( springs)$|( river )|( River)|( stream)|( Creek)|( creek)|( near )|( sea)$|( sea )|( Pool)|( pool)$|( City)|( reef )|( reef)$|( aquatic)$|( farm)|( Plateau)|( Bay)$|( Agua)")) %>%
  mutate(species = str_remove_all(species, "( Aquarium)| Province| province| state |(state)$|(plantation)$")) %>%
  mutate(species = str_remove_all(species, "(Western )|( South)")) %>%
  mutate(species = trimws(species)) %>%
  # location names
  mutate(species = str_remove_all(species, "(Adan)$| Adirondacks|( Australia)$|(Great Australian Bight)| Azores| Andai| Akaebi| Acla| Argis| Austria| Antalaha| Albanien| Almenara| Araguaia")) %>%
  mutate(species = str_remove_all(species, "( Benin)|( Bidou)|( Bissiang)|( Bioko)|( Bundu)|( Bush)$|(Bitter)|(Bivavotou)|(Bioko)| Beforana| Betampona|( Borneo)| Beysehir| Betari")) %>%
  mutate(species = str_remove_all(species, "(Cape )|(China )|( China)| Carombe|( Carib)$|( Cap Esterias)|(Chiba Museum)|( Chiba)$|(CabotCenter)| Continental| Cayman| Caracol| Calibasis| Chiriqui| Collier|( Caroline)| Contulmo| Chao Phraya|( Cana)| Columbia| Corrantijn")) %>%
  mutate(species = str_remove_all(species, " Girona| Gekara|(Greece)$|Guangdong|Guangxi|Guizhou|( Garcia)| Guinea| Ginbuna| Guyana| Gamba| Guama")) %>%
  mutate(species = str_remove_all(species, " Ivoloina|( Israel)| Ikorodu| Inji| Ijebu Ode|(Italy)| Izumihaze|(Iguassu)")) %>%
  mutate(species = str_remove_all(species, "(Kirk)$|( Kocher)|(Kipar)|(Kribi)|(Kuckuk)$|(Katsutoshi Watanabe)|(Komonyatsushihaze)|(Khukh)|(Kinbuna)| Karianga|(Kapinar)| Kieth| Kisangani| Kongou")) %>%
  mutate(species = str_remove_all(species, "( Lagos)|(Lebanon)$|( LoireLac)|(Liang Cao)| Lleida||(Lobaye)| Lucien")) %>%
    mutate(species = str_remove_all(species, "( Muerz)|( Malibo)| Mazinzi| Mfulgida| MinasBasin| MagdalenIs|( Mai)|( Mic)$|(Micnat)| MicRamrun| Mitsem| Madimba|(Madeira)| Mundemba| Machinda| Makuya|( Mexico)| Montenegro| Madagascar| Manjavacas| Makira| Martinique| Maranho| Moabi| Myanmar| Miya| Malinau| Manombo| Mahanara| Munday| Massana|(Masatoshi Nakamura)| Magdalena| Mongagu| Maroni| Martinso| Macacu| Maroa")) %>%
  mutate(species = str_remove_all(species, "(Nazilli)$| Ndombe| Ngombe| Nguru| Ndop| Nakuru| Nakabo|( Negro)$| Nevada| Nakabo| Nigeria| Nanay")) %>%
  mutate(species = str_remove_all(species, " Orinoco|( Oba)$|( Oyo)$")) %>%
  mutate(species = str_remove_all(species, " Patrocnica| Patchogue| Pachon|(Paris)| Pampang| Patrocnica| Patchogue| Pachon|(Pingxiang)| Paraguay| Paraguaza|( Peru)|( Panama)")) %>%
  mutate(species = str_remove_all(species, "(Rio Chirgua)| Ranomafana| Rakhine|( Rio)$|(Rio Sao Francisco)")) %>%
  mutate(species = str_remove_all(species, "( Suji)|( Suiyo)|( Smith)$|( Stevens)|(Shibukawa)| Salsburger| Surinam| Stepian| Stepien|(Sanya)|(Spain)$|( sagami)|(Santa Clara)| Scorff| Sahiler| Sambava| Samou|(Serra do Cip)")) %>%
  mutate(species = str_remove_all(species, "(Thalye)| tanukihaze|( Tres Marias)")) %>%
  mutate(species = str_remove_all(species, "(Ural)$|(United Kingdom)|( Urocara)|( Ulimi)| Uruguay")) %>%
  mutate(species = str_remove_all(species, "(Venezuela)|( Vanpoe)| Vevembe")) %>%
  mutate(species = str_remove_all(species, " Xingu")) %>%
  mutate(species = str_remove_all(species, "(Wainwright)$|( Whitewater)")) %>%
  mutate(species = str_remove_all(species, "( Yoma)|( Zagno)|( Zarco)|( Zhange)|(Zhang)$")) %>%
  mutate(species = trimws(species)) %>%
  # misc character strings that are left
  mutate(species = str_remove_all(species, "( Ac)$|(Ansp)$")) %>%
  mutate(species = str_remove_all(species, "(Blk)$|(Bl)$|( bn)$|( bl)$|( bw)$|( bac)$|( Bus)$")) %>%
  mutate(species = str_remove_all(species, "(CTo)$|( CrVb)|( Cr)$|(Cma)$|(Cp)$|( Chab)")) %>%
  mutate(species = str_remove_all(species, "( DaAm)$|( Dec)$|( dki)$|( dkic)|( dkiart)$|( dkisp)|( Dloop)$|( Dja)$")) %>%
  mutate(species = str_remove_all(species, "( Liz)$|(Lis)$|(La)$|(Lb)$|(Lc)$|(Ld)$|(Le)$|(Lau)$|(Lab)$|(Laf)|(Lra)$|(Lnas)")) %>%
   mutate(species = str_remove_all(species, "( No)|(No)$|(NanHai)|( Neo)$|(Nbre)|(Nb)$|(Nsa)$")) %>%
  mutate(species = str_remove_all(species, "( Tr)$|( trn)$|( trn )|(Tej)$|( Te)$|( Tk)$|( Tm)$( Tf)$|( Tq)$|( Tag)$|( Thr)|( Tht)$|( Thy )|( Thy)$|( Tru)$|( Truw)$|(TSUMAGUROSUJIHAZE)|(Twdate)( Tpra)$|( Tfla)$|( TrTp)$|( ThorAur)|( Tas)$|(TSA)")) %>%
  mutate(species = trimws(species)) %>%
  # random single lowercase letters
  mutate(species = str_remove_all(species, "( [a-z]{1})$")) %>%
  mutate(species = trimws(species)) %>%
  # final capital letter removal to mop up anything left
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  # in case multiple 'words'
  mutate(species = trimws(species)) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = trimws(species)) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_remove_all(species, "([A-Z])$")) %>%
  mutate(species = str_replace_all(species, 
                                   c('Corydoras C ' = 'Corydoras ',
                                     'Corydoras CW' = 'Corydoras '
                                     ))) %>%
  distinct() %>%
  rename(ncbi_sp = species,
         ncbi_uid = taxa_query)

```


## Expand NCBI results

Now that the Genbank accessions were turned to UIDs, its time to connect them to the other databases and update the actual taxonomy to match WoRMS and have OTL matches, like we did with invertebrates.


```{r ott ids}
# 1: TOL
#search only unique names
tol_search <- fish_ncbi_result %>%
  select(ncbi_sp) %>%
  distinct()

#tol resolve gives updated taxonomy and ott id
fish_resolved <- tol_resolve(tol_search$ncbi_sp) %>%
  mutate(search_string = str_to_sentence(search_string))

#set up to search worms
worms_search <- fish_resolved %>%
  mutate(tol_sp = coalesce(unique_name, search_string)) %>%
  select(tol_sp) %>%
  #remove any known introduction from tol
  mutate(tol_sp = str_replace_all(tol_sp, ' \\(species in Deuterostomia\\)|\\(genus in Deuterostomia\\)|\\(genus in Opisthokonta\\)|\\(genus in Holozoa\\)', "")) %>%
  mutate(tol_sp = str_replace_all(tol_sp, ' \\(species in domain Eukaryota\\)|ssp\\. \\([a-z]\\) MO-2000|\\(White, 1790\\)', "")) %>%
  mutate(tol_sp = trimws(tol_sp)) %>%
  mutate(species = tolower(tol_sp)) %>%
  distinct() %>%
  ## temporary issue requires replacing whitespace with '+'
  mutate(worms_query = gsub(" ", "+", species))


# 2: worms
fish_worms <- get_wormsid_(sci_com = worms_search$worms_query, marine_only = FALSE)
# get_wormsid_ gives back null and length 0 elements
## first remove with compact and discard then map_dfr
fish_worms2 <- fish_worms %>% 
  compact() %>%
  discard( ~ nrow(.x) == 0) %>%
  map_dfr( ~ data.frame(.x), .id = 'query')


# this cleaning step is relatively temporary until they fix the curl issue
fish_worms_result <- fish_worms2 %>%
  left_join(worms_search, by = c('query' = 'worms_query')) %>%
  relocate(species) %>%
  select(!(query)) %>%
  mutate(species = str_to_sentence(species))


# now match species to sciname to remove extra rows
fish_worms_result <- fish_worms_result %>%
  # remove higher taxonomy with species-level hits
  filter(!(str_detect(species, " ") == FALSE & str_detect(scientificname, " ") == TRUE)) %>%
  # removes species with subspecies level hits
  filter(!(!(species == scientificname))) %>%
  select(!(c(status))) %>%
  rename(worms_aphiaid = AphiaID,
        worms_sciname = scientificname) %>%
  distinct()


# extract higher and info about freshwater
fish_worms_records <- search_records_worms(fish_worms_result$worms_sciname)

# refine results to be useful
fish_worms_records2 <- fish_worms_records %>%
  # only animal hits
  filter(kingdom == 'Animalia') %>%
  # generate terrestrial-only and freshwater-only columns
  mutate(freshwater_only = ifelse((is_marine %in% c(0, NA) ==TRUE) & (is_brackish %in% c(0,NA) == TRUE) & (is_freshwater == 1),  "1", "0")) %>%
    mutate(terrestrial_only = ifelse((is_marine %in% c(0, NA) ==TRUE) & (is_brackish %in% c(0,NA) == TRUE) & (is_terrestrial == 1),  "1", "0")) %>%
  distinct() %>%
  # rename to format
  rename(taxa_query = query,
         worms_aphiaid = valid_aphia_id,
         original_aphiaid =aphia_id,
         worms_match = scientificname,
         worms_sciname = valid_name
         ) %>%
  # remove unneeded columns
  select(!(c(authority, parent_name_usage_id, is_freshwater, 
             is_terrestrial, is_marine, is_brackish, is_extinct, match_type))) %>%
  relocate(c(worms_sciname, worms_aphiaid), .before = original_aphiaid) %>%
  # rank lowercase
  mutate(rank = tolower(rank))

# 3: other databases

```

```{r}
#4: merge all and find problems
# join all updated fields
fish2 <- fish_ncbi_result %>%
  #select(taxa_query, ncbi_sp) %>%
  #rename(ncbi_uid = taxa_query) %>%
  left_join(fish_resolved, by = c('ncbi_sp' = 'search_string')) %>%
  rename(tol_sp = unique_name) %>%
  left_join(fish_worms_records2, by = c('tol_sp' = 'taxa_query')) %>%
  select(!(c(kingdom, phylum, number_matches))) %>%
  relocate(c('worms_aphiaid', 'original_aphiaid', 'ncbi_uid', 'ott_id'), .before = 'class') %>%
  relocate(c('rank', 'worms_sciname', 'worms_match', 'tol_sp', 'ncbi_sp')) %>%
  #single column for TOL and WORMS replacements; bold and gbif tend to follow TOL
  mutate(found_taxa = coalesce(worms_sciname, tol_sp)) %>%
  relocate('found_taxa') %>%
  select(!(c(worms_match, original_aphiaid)))

#write full
write.csv(fish2, here(rosetta, 'taxize', '20221108_fish_taxonomy-full.csv'))
```

# Problems

NCBI data is dirty and also, many fish aren't found in WoRMS despite being real.

First though we'll find the species in worms but NOT open tree of life.

```{r problems-worms}
# read in draft if necessary
fish2 <- read_csv(here(rosetta, 'taxize', '20221108_fish_taxonomy-full.csv'))[-1]

# extract 'failures'
fish_fail_worms <- fish2 %>%
  # not found in TOL or WoRMS
  #filter(is.na(found_taxa)) %>%
  # not found in WoRMS:
  ## note that anything not found in TOL was not passed to worms!
  filter(is.na(worms_sciname)) %>%
  select(ncbi_sp) %>%
  distinct() %>%
  ## temporary issue requires replacing whitespace with '+'
  mutate(species = tolower(ncbi_sp)) %>%
  mutate(worms_query = gsub(" ", "+", species))


# 1) recover anything obvious in worms but not tol:
fish_worms <- get_wormsid_(sci_com = fish_fail_worms$worms_query, marine_only = FALSE)
# get_wormsid_ gives back null and length 0 elements
## first remove with compact and discard then map_dfr
fish_worms2 <- fish_worms %>% 
  compact() %>%
  discard( ~ nrow(.x) == 0) %>%
  map_dfr( ~ data.frame(.x), .id = 'query')


# this cleaning step is relatively temporary until they fix the curl issue
fish_worms_result <- fish_worms2 %>%
  left_join(fish_fail_worms, by = c('query' = 'worms_query')) %>%
  relocate(species) %>%
  select(!(query)) %>%
  mutate(species = str_to_sentence(species))


# now match species to sciname to remove extra rows
fish_worms_result <- fish_worms_result %>%
  # remove higher taxonomy with species-level hits
  filter(!(str_detect(species, " ") == FALSE & str_detect(scientificname, " ") == TRUE)) %>%
  # removes species with subspecies level hits
  filter(!(!(species == scientificname))) %>%
  select(!(c(status))) %>%
  rename(worms_aphiaid = AphiaID,
        worms_sciname = scientificname) %>%
  distinct()

# extract higher and info about freshwater
fish_worms_records <- search_records_worms(fish_worms_result$worms_sciname)

# refine results to be useful
fish_worms_records2 <- fish_worms_records %>%
  # only animal hits
  filter(kingdom == 'Animalia') %>%
  # generate terrestrial-only and freshwater-only columns
  mutate(freshwater_only = ifelse((is_marine %in% c(0, NA) ==TRUE) & (is_brackish %in% c(0,NA) == TRUE) & (is_freshwater == 1),  "1", "0")) %>%
    mutate(terrestrial_only = ifelse((is_marine %in% c(0, NA) ==TRUE) & (is_brackish %in% c(0,NA) == TRUE) & (is_terrestrial == 1),  "1", "0")) %>%
  distinct() %>%
  # rename to format
  rename(taxa_query = query,
         worms_aphiaid = valid_aphia_id,
         original_aphiaid =aphia_id,
         worms_match = scientificname,
         worms_sciname = valid_name
         ) %>%
  # remove unneeded columns
  select(!(c(authority, parent_name_usage_id, is_freshwater, 
             is_terrestrial, is_marine, is_brackish, is_extinct, match_type))) %>%
  relocate(c(worms_sciname, worms_aphiaid), .before = original_aphiaid) %>%
  # rank lowercase
  mutate(rank = tolower(rank)) %>%
  rename(ncbi_sp = taxa_query) %>%
  select(!(c(kingdom, phylum, worms_match, original_aphiaid))) %>%
  mutate(found_taxa = worms_sciname)


# merge back into fish2
fish3 <- fish2 %>%
  filter(!(ncbi_sp %in% fish_worms_records2$ncbi_sp)) %>%
  bind_rows(fish_worms_records2)


#overwrite full
write.csv(fish3, here(rosetta, 'taxize', '20221108_fish_taxonomy-full.csv'))
```

## Genus-level

Now we will assign higher taxonomy to things with a tol id to genus level
split tol to genus then just match existing 

```{r tol-genus}
# get worms info for genera
## everything not found in worms, search at the generic level
genera_tol <- fish3 %>%
  filter(is.na(worms_aphiaid)) %>%
  # everything from the dataframe we want to keep
  select(found_taxa, tol_sp, ncbi_sp, approximate_match, 
         is_synonym, flags, ncbi_uid, ott_id) %>%
  distinct() %>%
  filter(!(is.na(found_taxa))) %>%
  separate(found_taxa, into = 'genus', 
           sep = " ", remove = FALSE, 
           extra = 'drop') 

# select generic level worms matches to match extracted genus
worms_match <- fish3 %>%
  filter(rank %in% c('genus')) %>%
  # remove everything from the dataframe that will be populated by tol
  select(!(c(found_taxa, tol_sp, ncbi_sp, approximate_match, 
         is_synonym, flags, ncbi_uid, ott_id))) %>%
  distinct()

# speces level extracting genus
worms_match2 <- fish3 %>%
    filter(rank %in% c('species')) %>%
  # remove everything from the dataframe that will be populated by tol
  select(!(c(found_taxa, tol_sp, ncbi_sp, approximate_match, 
         is_synonym, flags, ncbi_uid, ott_id))) %>%
  # remove columns that are specific to species
  select(!(c(valid_authority, worms_aphiaid, unacceptreason, status, freshwater_only, terrestrial_only))) %>%
  distinct() %>%
  mutate(worms_sciname = genus) %>%
  mutate(rank = 'genus') %>%
  distinct() %>%
  filter(!(worms_sciname %in% worms_match$worms_sciname)) %>%
  bind_rows(worms_match)
  


genera_tol_match <- genera_tol %>%
  left_join(worms_match2) %>%
  distinct()


# merge back into fish3
fish4 <- fish3 %>%
  filter(!(found_taxa %in% genera_tol_match$found_taxa)) %>%
  bind_rows(genera_tol_match) %>%
  # right now these all seem like duplicates?
  filter(!(status %in% c('unaccepted')))


#overwrite full
write.csv(fish3, here(rosetta, 'taxize', '20221108_fish_taxonomy-full.csv'))

```


It seems that all genera aren't in the list so we'll do a worms search at the generic level for any genus that might be missing
Some
```{r tol-genus worms-search}
genera_missing <- fish4 %>%
  filter(is.na(worms_sciname)) %>%
  filter(!(is.na(genus))) %>%
  select(genus) %>%
  distinct()


fish_worms <- get_wormsid_(sci_com = genera_missing$genus, marine_only = FALSE)
# get_wormsid_ gives back null and length 0 elements
## first remove with compact and discard then map_dfr
fish_worms2 <- fish_worms %>% 
  compact() %>%
  discard( ~ nrow(.x) == 0) %>%
  map_dfr( ~ data.frame(.x), .id = 'query')

```






## continued problems

A lot of these are misspellings so another round of cleaning the original data will resolve them.
But until then we'll check other databases
```{r problems-gbif}
# extract 'failures'
fish_fail_all <- fish3 %>%
  # not found in TOL or WoRMS
  filter(is.na(found_taxa)) %>%
  # not found in WoRMS:
  ## note that anything not found in TOL was not passed to worms!
  #filter(is.na(worms_sciname)) %>%
  select(ncbi_sp) %>%
  distinct()

# GBIF id
fish_gbifid <- get_gbifid_(sci = fish_fail_all$ncbi_sp, rows = 1)

fish_gbifid2 <- map_dfr(.x= fish_gbifid, ~ data.frame(.x), .id = 'taxa_query') %>%
  filter(kingdom == "Animalia") %>%
  # eliminating fuzzy matches for now
  filter(matchtype == 'EXACT') %>%
  # strip higher taxonomy from gbif bc it doesn't match worms/bold
  ## but keep keys!
  select(!(c(kingdom, phylum, class, order, scientificname,
             status, confidence, matchtype, kingdomkey,
             # just keeping regular gbif key
             acceptedusagekey, phylumkey, orderkey,
             classkey, familykey, genuskey, specieskey,
             synonym, note))) %>%
    rename(gbif_key = usagekey,
         gbif_sciname = canonicalname)


# get worms info for genera
## everything not found in worms, search at the generic level
genera_worms <- fish3 %>%
  filter(is.na(worms_aphiaid)) %>%
  select(found_taxa) %>%
  distinct() %>%
  filter(!(is.na(found_taxa))) %>%
  separate(found_taxa, into = 'genus', 
           sep = " ", remove = TRUE, 
           extra = 'drop') %>%
  bind_rows(fish_gbifid2) %>%
  select(genus) %>%
  distinct()


# 1) recover anything obvious in worms but not tol:
fish_worms <- get_wormsid_(sci_com = genera_worms$genus)
# get_wormsid_ gives back null and length 0 elements
## first remove with compact and discard then map_dfr
fish_worms2 <- fish_worms %>% 
  compact() %>%
  discard( ~ nrow(.x) == 0) %>%
  map_dfr( ~ data.frame(.x), .id = 'query')

# this cleaning step is relatively temporary until they fix the curl issue
fish_worms_result <- fish_worms2 %>%
  # only not-species
  filter(str_detect(scientificname, " ") == FALSE) %>%
  rename(worms_aphiaid = AphiaID,
        worms_sciname = scientificname) #%>%
  select(!(c(status, query))) %>%
  distinct()


# extract higher and info about freshwater
fish_worms_records <- search_records_worms(fish_worms_result$worms_sciname)

# refine results to be useful
fish_worms_records2 <- fish_worms_records %>%
  # only animal hits
  filter(kingdom == 'Animalia') %>%
  # generate terrestrial-only and freshwater-only columns
  mutate(freshwater_only = ifelse((is_marine %in% c(0, NA) ==TRUE) & (is_brackish %in% c(0,NA) == TRUE) & (is_freshwater == 1),  "1", "0")) %>%
    mutate(terrestrial_only = ifelse((is_marine %in% c(0, NA) ==TRUE) & (is_brackish %in% c(0,NA) == TRUE) & (is_terrestrial == 1),  "1", "0")) %>%
  distinct() %>%
  # rename to format
  rename(taxa_query = query,
         worms_aphiaid = valid_aphia_id,
         original_aphiaid =aphia_id,
         worms_match = scientificname,
         worms_sciname = valid_name
         ) %>%
  # remove unneeded columns
  select(!(c(authority, parent_name_usage_id, is_freshwater, 
             is_terrestrial, is_marine, is_brackish, is_extinct, match_type))) %>%
  relocate(c(worms_sciname, worms_aphiaid), .before = original_aphiaid) %>%
  # rank lowercase
  mutate(rank = tolower(rank)) %>%
  rename(ncbi_sp = taxa_query) %>%
  select(!(c(kingdom, phylum, worms_match, original_aphiaid))) %>%
  mutate(found_taxa = worms_sciname)




```


