---
title: "taxize-merge"
author: "Kate Sheridan"
date: '2022-06-27'
output: html_document
---

Ideally at this point, we've fixed all the problems and found all the taxonomy.

Here we're going to merge fixed problems back into the original taxonomy_full files, and merge all files to full database, and then we'll have a working key draft.

We're also going to generate a list of terrestrial and freshwater only groups, so that projects that don't use the key can still benefit from the searches done.

```{r setup, include=FALSE}
library(tidyverse)
library(here)

# here filepaths
problems <- here('species_lists', 'hakai', '2022rosetta', 'problems')
rosetta <- here('species_lists', 'hakai', '2022rosetta')
tol_conflict <- here('species_lists', 'hakai', '2022rosetta', 'problems', 'tol_conflict')
```

# load in previous
```{r load in}
annelid <- read_csv(here(rosetta, 'taxize',
                         '20220718_annelid_taxonomy-full.csv'))[-1]
arthropod <- read_csv(here(rosetta, 'taxize',
                         '20220718_arthropod_taxonomy-full.csv'))[-1]
chordata <- read_csv(here(rosetta, 'taxize',
                         '20220718_chordata_taxonomy-full.csv'))[-1]
mollusca <- read_csv(here(rosetta, 'taxize',
                         '20220718_mollusca_taxonomy-full.csv'))[-1]
ech_platy_nem <- read_csv(here(rosetta, 'taxize',
                         '20220718_ech_platy_nem_taxonomy-full.csv'))[-1]
smallphyla <- read_csv(here(rosetta, 'taxize',
                         '20220718_smallphyla_taxonomy-full.csv'))[-1]

# merge all tables
all_taxa <- full_join(annelid, arthropod) %>%
  full_join(chordata) %>%
  full_join(mollusca) %>%
  full_join(ech_platy_nem) %>%
  full_join(smallphyla)
```


# load in fixed


```{r load-in-resolved}
annelid_res <- read_csv(here(problems, 'resolved',
                         '20220719_annelid_worms_tol-resolved.csv'))
arthropod_res <- read_csv(here(problems, 'resolved',
                         '20220719_arthropod_worms_tol-resolved.csv'))
chordata_res <- read_csv(here(problems, 'resolved',
                         '20220719_chordata_worms_tol-resolved.csv'))
mollusca_res <- read_csv(here(problems, 'resolved',
                         '20220719_mollusca_worms_tol-resolved.csv'))
ech_platy_nem_res <- read_csv(here(problems, 'resolved',
                         '20220719_ech_platy_nem_worms_tol-resolved.csv'))
smallphyla_res <- read_csv(here(problems, 'resolved',
                         '20220719_smallphyla_worms_tol-resolved.csv'))


# merge all tables
all_taxa_res <- full_join(annelid_res, arthropod_res) %>%
  full_join(chordata_res) %>%
  full_join(mollusca_res) %>%
  full_join(ech_platy_nem_res) %>%
  full_join(smallphyla_res) %>%
  relocate(taxa_query)


# resolved round 2, load in


# merge round 2 with round 1
```


# join first and second round of resolved
Note the second round hasn't been done yet so its just the first one for now (july 21 2022)

```{r join problems}
all_taxa_res2 <- full_join(all_taxa_res, all_taxa) %>%
  #join second round here
  #its all animals so kingdom is unnecessary
  select(!(kingdom))

#save!
write_csv(all_taxa_res2, here(rosetta, 'current_draft',
                              '20220721_blast-db_taxonomy-all.csv'))
```


# freshwater and terrestrial keys

```{r freshwater-terrestrial}
# filter to any taxa with only freshwater or terrestrial == true
all_freshterr <- all_taxa_res2 %>%
  filter(terrestrial_only == 1 | freshwater_only == 1)

# save!  
write_csv(all_freshterr, here('latest-keys', '20220721_freshwater_terrestrial.csv'))
```



# scratch

If I need to read it back in to mess around with options
```{r}

all_taxa_res2<-read_csv(here(rosetta, 'current_draft',
                              '20220704_blast-db_taxonomy-all.csv'))
```




