---
title: "hakai-db taxize fix 2"
author: "Kate Sheridan"
date: '2022-06-30'
output: html_document
---

Here we'll load in all the outstanding problems to be manually resolved

```{r setup, include=FALSE}
library(tidyverse)
library(stringr)
library(taxize)
library(here)

# here filepaths
# here filepaths
problems <- here('species_lists', 'hakai', '2022rosetta', 'problems')
rosetta <- here('species_lists', 'hakai', '2022rosetta')
tol_conflict <- here('species_lists', 'hakai', '2022rosetta', 'problems', 'tol_conflict')
```


# tol-worms family level conflicts

Some of the conflicts are at the family or genus level.
First we resolve the ones we know about; if genus in fresh/terrestrial file then add anything from not-found. Then we'll see what's left, look them up at a family level, manually add them ot fresh/terrestrial. if marine, set aside for later.

```{r annelid-loadin}
annelid_freshterr <- read_csv(here(problems, 'fresh_terrestrial',
                                   '20220630_annelid_fresh-terr.csv'))

annelid_family <- read_csv(here(tol_conflict,
                                        '20220630_annelid_worms_tol-conflict-family.csv'))

annelid_notfound <- read_csv(here(problems, 'not_found',
                                        '20220624_annelid_not-found.csv'))[-1]%>%
  rename(query = taxa)

annelid_notfound_tol <- read_csv(here(problems, 'not_found',
                                        '20220630_annelid_not_found-tol.csv')) 


annelid_conflicts <- full_join(annelid_notfound, annelid_family) %>%
  relocate(query) %>%
  full_join(annelid_notfound_tol)
```


```{r annelid-freshterr}
# list of freshwater/terrestrial genera
annelid_freshterr_gen <- annelid_freshterr %>%
  select(genus_split, freshwater_only, terrestrial_only) %>%
  distinct()

# filter for known fresh/terr genera
annelid_conflicts2 <- annelid_conflicts %>%
  filter(!(is.na(query))) %>%
  # extract genus names so we can test them
  separate(query, into = 'genus_split', " ", 1, 
           remove = FALSE, extra = 'drop') %>%
  select(!(c(is_marine, is_freshwater, is_brackish, is_terrestrial))) %>%
  left_join(annelid_freshterr_gen)

# merge generic level finds to original
annelid_freshterr2 <- annelid_conflicts2 %>%
  filter(!((freshwater_only %in% c(NA)) & (terrestrial_only %in% c(NA)))) %>%
  select(query, phylum, class, order, family, genus_split,
         freshwater_only, terrestrial_only) %>%
  rename(taxa_query = query) %>%
  full_join(annelid_freshterr)

# look at remaining
annelid_conflicts_family <- annelid_conflicts %>%
  filter(!(query %in% annelid_freshterr2$taxa_query)) %>%
  select(family) %>%
  distinct()


# manually populate freshwater, terrestrial, and marine columns
annelid_conflicts_family <- annelid_conflicts_family %>%
  mutate(freshwater_only = ifelse(family %in% c('Branchiobdellidae', 'Glossiphoniidae',
                                                'Lumbriculidae', 'Cylicobdellidae',
                                                'Hirudinidae', 'Orobdellidae',
                                                'Gastrostomobdellidae', 
                                                'Salifidae', 'Semiscolecidae',
                                                'Xerobdellidae'), '1', 
                                  ifelse(family %in% c('Almidae', 'Acanthodrilidae', 'Dorvilleidae',
                                                       'Eunicidae', 'Flabelligeridae',
                                                       'Golfingiidae', 'Hesionidae',
                                                       'Haemadipsidae',
                                                       'Lumbricidae', 'Hormogastridae',
                                                       'Lumbrineridae', 'Maldanidae',
                                                       'Megascolecidae', 'Myzostomatidae',
                                                       'Nephtyidae', 'Paraonidae',
                                                       'Phascolosomatidae', 'Phascolionidae',
                                                       'Phyllodocidae',
                                                       'Polynoidae', 'Sabellariidae',
                                                       'Siboglinidae', 'Spionidae',
                                                       'Sipunculidae','Syllidae', 'Themistidae'), '0', NA))) %>%
  mutate(terrestrial_only = ifelse(family %in% c('Americobdellidae', 'Almidae', 'Acanthodrilidae',
                                                 'Hormogastridae', 'Cylicobdellidae',
                                                 'Lumbricidae', 'Cicadellidae',
                                                 'Megascolecidae', 'Haemadipsidae',
                                                 'Orobdellidae', 'Octochaetidae', 'Xerobdellidae'), '1', 
                                  ifelse(family %in% c('Branchiobdellidae', 
                                                       'Dorvilleidae', 'Eunicidae',
                                                       'Flabelligeridae', 'Glossiphoniidae',
                                                       'Golfingiidae', 'Hesionidae',
                                                       'Hirudinidae', 'Lumbrineridae',
                                                       'Maldanidae', 'Myzostomatidae',
                                                       'Nephtyidae', 'Paraonidae',
                                                       'Phascolosomatidae', 'Phascolionidae',
                                                       'Phyllodocidae',
                                                       'Piscicolidae', 'Polynoidae',
                                                       'Sipunculidae','Syllidae', 'Salifidae',
                                                       'Serpulidae', 'Siboglinidae',
                                                       'Sabellariidae', 'Semiscolecidae',
                                                       'Spionidae', 'Lumbriculidae', 'Themistidae'),
                                         '0', NA))) %>%
  mutate(is_marine = ifelse(family %in% c('Dorvilleidae','Eunicidae', 'Flabelligeridae',
                                          'Golfingiidae', 'Hesionidae', 'Lumbrineridae',
                                          'Maldanidae', 'Myzostomatidae', 'Nephtyidae',
                                          'Paraonidae', 'Phascolosomatidae', 'Phascolionidae',
                                          'Phyllodocidae', 'Polynoidae', 'Sabellariidae',
                                          'Siboglinidae', 'Spionidae',
                                          'Sipunculidae','Syllidae', 'Themistidae'), '1', 
                                  ifelse(family %in% c('Lumbriculidae', 'Almidae', 'Acanthodrilidae',
                                                       'Branchiobdellidae', 'Americobdellidae',
                                                       'Cylicobdellidae',
                                                       'Glossiphoniidae', 'Hirudinidae',
                                                       'Haemadipsidae', 'Gastrostomobdellidae',
                                                       'Lumbricidae', 'Hormogastridae',
                                                       'Megascolecidae', 'Octochaetidae',
                                                       'Salifidae', 'Semiscolecidae',
                                                       'Xerobdellidae'), '0', NA)))

# note; some marine but not all: Enchytraeidae, Naididae, Nereididae, piscicolidae, Serpulidae
# note themistidae, phascolionidae unaccepted; now golfingiidae

# filter conflicts again, merge with previous list
annelid_freshterr3 <- annelid_conflicts %>%
  filter(!(query %in% annelid_freshterr2$taxa_query)) %>%
  select(!(c(is_marine, is_freshwater, is_brackish, is_terrestrial))) %>%
  left_join(annelid_conflicts_family) %>%
  select(query, phylum, class, order, family,
         freshwater_only, terrestrial_only) %>%
  filter(freshwater_only == 1 | terrestrial_only == 1) %>%
  mutate(freshwater_only = as.numeric(freshwater_only)) %>%
  mutate(terrestrial_only = as.numeric(terrestrial_only)) %>%
  rename(taxa_query = query) %>%
  full_join(annelid_freshterr2)

write_csv(annelid_freshterr3, here(problems, 'fresh_terrestrial',
                                   '20220704_annelid_fresh-terr.csv'))

```

```{r annelid-manual}
# what's left is potentially marine but still not found in worms
## note that quick checks show freshwater, entirely not found, and genus (subgenus) species issues.
annelid_conflicts4 <- annelid_conflicts %>%
  filter(!(query %in% annelid_freshterr3$taxa_query))

write_csv(annelid_conflicts4, here(problems, 'not_found',
                                   '20220704_annelid_not-found_outstanding.csv'))
```




# arthropods

```{r arthropods-loadin}
arthropod_freshterr <- read_csv(here(problems, 'fresh_terrestrial',
                                   '20220630_arthropod_fresh-terr.csv'))

arthropod_family <- read_csv(here(tol_conflict,
                                        '20220630_arthropod_worms_tol-conflict-family.csv'))

arthropod_notfound <- read_csv(here(problems, 'not_found',
                                        '20220624_arthropod_not-found.csv'))[-1] %>%
  rename(query = taxa)

arthropod_notfound_tol <- read_csv(here(problems, 'not_found',
                                        '20220630_arthropod_not_found-tol.csv')) 

arthropod_conflicts <- full_join(arthropod_notfound, arthropod_family) %>%
  relocate(query) %>%
  full_join(arthropod_notfound_tol)
```



```{r}
# list of freshwater/terrestrial genera
arthropod_freshterr_gen <- arthropod_freshterr %>%
  select(genus_split, freshwater_only, terrestrial_only) %>%
  distinct()

# filter for known fresh/terr genera
arthropod_conflicts2 <- arthropod_conflicts %>%
  filter(!(is.na(query))) %>%
  # extract genus names so we can test them
  separate(query, into = 'genus_split', " ", 1, 
           remove = FALSE, extra = 'drop') %>%
  select(!(c(is_marine, is_freshwater, is_brackish, is_terrestrial))) %>%
  left_join(arthropod_freshterr_gen)

# merge generic level finds to original
arthropod_freshterr2 <- arthropod_conflicts2 %>%
  filter(!((freshwater_only %in% c(NA)) & (terrestrial_only %in% c(NA)))) %>%
  select(query, phylum, class, order, family, genus_split,
         freshwater_only, terrestrial_only) %>%
  rename(taxa_query = query) %>%
  full_join(arthropod_freshterr)

# look at remaining
# start with order for arthropods
arthropod_conflicts_order <- arthropod_conflicts %>%
  filter(!(query %in% arthropod_freshterr2$taxa_query)) %>%
  select(order) %>%
  distinct()


# manually populate freshwater, terrestrial, and marine columns
arthropod_conflicts_order <- arthropod_conflicts_order %>%
  mutate(freshwater_only = ifelse(order %in% c(), '1', 
                                  ifelse(order %in% c('Cumacea','Opiliones'), '0', NA))) %>%
  mutate(terrestrial_only = ifelse(order %in% c('Opiliones'), '1', 
                                  ifelse(order %in% c('Cumacea'), '0', NA))) %>%
  mutate(is_marine = ifelse(order %in% c('Cumacea'), '1', 
                                  ifelse(order %in% c('Opiliones'), '0', NA)))


# filter conflicts again, merge with previous list
arthropod_freshterr3 <- arthropod_conflicts %>%
  filter(!(query %in% arthropod_freshterr2$taxa_query)) %>%
  select(!(c(is_marine, is_freshwater, is_brackish, is_terrestrial))) %>%
  left_join(arthropod_conflicts_order) %>%
  select(query, phylum, class, order, family,
         freshwater_only, terrestrial_only) %>%
  filter(freshwater_only == 1 | terrestrial_only == 1) %>%
  mutate(freshwater_only = as.numeric(freshwater_only)) %>%
  mutate(terrestrial_only = as.numeric(terrestrial_only)) %>%
  rename(taxa_query = query) %>%
  full_join(arthropod_freshterr2)

write_csv(arthropod_freshterr3, here(problems, 'fresh_terrestrial',
                                   '20220704_arthropod_fresh-terr.csv'))
```


```{r}
arthropod_conflicts4 <- arthropod_conflicts %>%
  filter(!(query %in% arthropod_freshterr3$taxa_query))

write_csv(arthropod_conflicts4, here(problems, 'not_found',
                                   '20220704_arthropod_not-found_outstanding.csv'))
```




# Chordata

Chordates did not have conflicts at the family level. Instead, the only not-found 

```{r}
chordata_freshterr <- read_csv(here(problems, 'fresh_terrestrial',
                                   '20220630_chordata_fresh-terr.csv'))

#chordata_family <- read_csv(here(tol_conflict,
#                                        '20220630_chordata_worms_tol-conflict-family.csv'))

chordata_notfound <- read_csv(here(problems, 'not_found',
                                        '20220624_chordata_not-found.csv'))[-1] %>%
  rename(query = taxa)

chordata_notfound_tol <- read_csv(here(problems, 'not_found',
                                        '20220630_chordata_not_found-tol.csv')) 

#chordata_conflicts <- full_join(chordata_notfound, chordata_family) %>%
#  relocate(query)

# no family level conflicts?
chordata_conflicts <- chordata_notfound
```


```{r chordata-manual}


```


# Mollusca

```{r}

mollusca_freshterr <- read_csv(here(problems, 'fresh_terrestrial',
                                   '20220630_mollusca_fresh-terr.csv'))

mollusca_family <- read_csv(here(tol_conflict,
                                        '20220630_mollusca_worms_tol-conflict-family.csv'))

mollusca_notfound <- read_csv(here(problems, 'not_found',
                                        '20220624_mollusca_not-found.csv'))[-1] %>%
  rename(query = taxa)

mollusca_notfound_tol <- read_csv(here(problems, 'not_found',
                                        '20220630_mollusca_not_found-tol.csv')) 

mollusca_conflicts <- full_join(mollusca_notfound, mollusca_family) %>%
  relocate(query) %>%
  full_join(mollusca_notfound_tol)
```



```{r mollusca-freshterr}
# list of freshwater/terrestrial genera
mollusca_freshterr_gen <- mollusca_freshterr %>%
  select(genus_split, freshwater_only, terrestrial_only) %>%
  distinct()

# filter for known fresh/terr genera
mollusca_conflicts2 <- mollusca_conflicts %>%
  filter(!(is.na(query))) %>%
  # extract genus names so we can test them
  separate(query, into = 'genus_split', " ", 1, 
           remove = FALSE, extra = 'drop') %>%
  select(!(c(is_marine, is_freshwater, is_brackish, is_terrestrial))) %>%
  left_join(mollusca_freshterr_gen)

# merge generic level finds to original
mollusca_freshterr2 <- mollusca_conflicts2 %>%
  filter(!((freshwater_only %in% c(NA)) & (terrestrial_only %in% c(NA)))) %>%
  select(query, phylum, class, order, family, genus_split,
         freshwater_only, terrestrial_only) %>%
  rename(taxa_query = query) %>%
  full_join(mollusca_freshterr)

# look at remaining
# start with order for molluscas
mollusca_conflicts_order <- mollusca_conflicts %>%
  filter(!(query %in% mollusca_freshterr2$taxa_query)) %>%
  select(order) %>%
  distinct()


# manually populate freshwater, terrestrial, and marine columns
mollusca_conflicts_order <- mollusca_conflicts_order %>%
  mutate(freshwater_only = ifelse(order %in% c(), '1', 
                                  ifelse(order %in% c('Cumacea','Opiliones'), '0', NA))) %>%
  mutate(terrestrial_only = ifelse(order %in% c('Opiliones'), '1', 
                                  ifelse(order %in% c('Cumacea'), '0', NA))) %>%
  mutate(is_marine = ifelse(order %in% c('Cumacea'), '1', 
                                  ifelse(order %in% c('Opiliones'), '0', NA)))


# filter conflicts again, merge with previous list
mollusca_freshterr3 <- mollusca_conflicts %>%
  filter(!(query %in% mollusca_freshterr2$taxa_query)) %>%
  select(!(c(is_marine, is_freshwater, is_brackish, is_terrestrial))) %>%
  left_join(mollusca_conflicts_order) %>%
  select(query, phylum, class, order, family,
         freshwater_only, terrestrial_only) %>%
  filter(freshwater_only == 1 | terrestrial_only == 1) %>%
  mutate(freshwater_only = as.numeric(freshwater_only)) %>%
  mutate(terrestrial_only = as.numeric(terrestrial_only)) %>%
  rename(taxa_query = query) %>%
  full_join(mollusca_freshterr2)

write_csv(mollusca_freshterr3, here(problems, 'fresh_terrestrial',
                                   '20220704_mollusca_fresh-terr.csv'))
```

```{r}
mollusca_conflicts4 <- mollusca_conflicts %>%
  filter(!(query %in% mollusca_freshterr3$taxa_query)) 

write_csv(mollusca_conflicts4, here(problems, 'not_found',
                                   '20220704_mollusca_not-found_outstanding.csv'))
```



# Echinoderms, platyhelminthes, Nemerteans

```{r}
ech_platy_nem_freshterr <- read_csv(here(problems, 'fresh_terrestrial',
                                   '20220630_ech_platy_nem_fresh-terr.csv'))

ech_platy_nem_family <- read_csv(here(tol_conflict,
                                        '20220630_ech_platy_nem_worms_tol-conflict-family.csv'))

ech_platy_nem_notfound <- read_csv(here(problems, 'not_found',
                                        '20220624_ech_platy_nem_not-found.csv'))[-1] %>%
  rename(query = taxa)

ech_platy_nem_notfound_tol <- read_csv(here(problems, 'not_found',
                                        '20220630_ech_platy_nem_not_found-tol.csv')) 

ech_platy_nem_conflicts <- full_join(ech_platy_nem_notfound, ech_platy_nem_family) %>%
  relocate(query) %>%
  full_join(ech_platy_nem_notfound_tol)
```


```{r echplatynem-freshterr}
# list of freshwater/terrestrial genera
ech_platy_nem_freshterr_gen <- ech_platy_nem_freshterr %>%
  select(genus_split, freshwater_only, terrestrial_only) %>%
  distinct()

# filter for known fresh/terr genera
ech_platy_nem_conflicts2 <- ech_platy_nem_conflicts %>%
  filter(!(is.na(query))) %>%
  # extract genus names so we can test them
  separate(query, into = 'genus_split', " ", 1, 
           remove = FALSE, extra = 'drop') %>%
  select(!(c(is_marine, is_freshwater, is_brackish, is_terrestrial))) %>%
  left_join(ech_platy_nem_freshterr_gen)

# merge generic level finds to original
ech_platy_nem_freshterr2 <- ech_platy_nem_conflicts2 %>%
  filter(!((freshwater_only %in% c(NA)) & (terrestrial_only %in% c(NA)))) %>%
  select(query, phylum, class, order, family, genus_split,
         freshwater_only, terrestrial_only) %>%
  rename(taxa_query = query) %>%
  full_join(ech_platy_nem_freshterr)

# look at remaining
# start with order for ech_platy_nems
ech_platy_nem_conflicts_order <- ech_platy_nem_conflicts %>%
  filter(!(query %in% ech_platy_nem_freshterr2$taxa_query)) %>%
  select(order) %>%
  distinct()


# manually populate freshwater, terrestrial, and marine columns
ech_platy_nem_conflicts_order <- ech_platy_nem_conflicts_order %>%
  mutate(freshwater_only = ifelse(order %in% c(), '1', 
                                  ifelse(order %in% c('Araneae', 'Ophiurida'), '0', NA))) %>%
  mutate(terrestrial_only = ifelse(order %in% c('Araneae'), '1', 
                                  ifelse(order %in% c('Ophiurida'), '0', NA))) %>%
  mutate(is_marine = ifelse(order %in% c('Ophiurida'), '1', 
                                  ifelse(order %in% c('Araneae'), '0', NA)))%>%
  mutate(internal_parasite = ifelse(order %in% c('Cyclophyllidea'), '1', 
                                  ifelse(order %in% c('Ophiurida'), '0', NA))) %>%
  mutate(is_marine = as.numeric(is_marine))

# filter conflicts again, merge with previous list
ech_platy_nem_freshterr3 <- ech_platy_nem_conflicts %>%
  filter(!(query %in% ech_platy_nem_freshterr2$taxa_query)) %>%
  select(!(c(is_marine, is_freshwater, is_brackish, is_terrestrial))) %>%
  left_join(ech_platy_nem_conflicts_order) %>%
  select(query, phylum, class, order, family,
         freshwater_only, terrestrial_only) %>%
  filter(freshwater_only == 1 | terrestrial_only == 1) %>%
  mutate(freshwater_only = as.numeric(freshwater_only)) %>%
  mutate(terrestrial_only = as.numeric(terrestrial_only)) %>%
  rename(taxa_query = query) %>%
  full_join(ech_platy_nem_freshterr2)

write_csv(ech_platy_nem_freshterr3, here(problems, 'fresh_terrestrial',
                                   '20220704_ech_platy_nem_fresh-terr.csv'))



ech_platy_nem_parasites <- ech_platy_nem_conflicts %>%
  left_join(ech_platy_nem_conflicts_order) %>%
  filter(internal_parasite == 1) %>%
  select(query, phylum, class, order, family,
         internal_parasite)


write_csv(ech_platy_nem_parasites, here(problems, 'fresh_terrestrial',
                                   '20220704_ech_platy_nem_internal-parasites.csv'))
```


```{r}
ech_platy_nem_conflicts4 <- ech_platy_nem_conflicts %>%
  filter(!(query %in% ech_platy_nem_freshterr3$taxa_query)) %>%
  filter(!(query %in% ech_platy_nem_parasites$query))

write_csv(ech_platy_nem_conflicts4, here(problems, 'not_found',
                                   '20220704_ech_platy_nem_not-found_outstanding.csv'))
```




# Small Phyla

```{r}
smallphyla_freshterr <- read_csv(here(problems, 'fresh_terrestrial',
                                   '20220630_smallphyla_fresh-terr.csv'))

smallphyla_family <- read_csv(here(tol_conflict,
                                        '20220630_smallphyla_worms_tol-conflict-family.csv'))

smallphyla_notfound <- read_csv(here(problems, 'not_found',
                                        '20220624_smallphyla_not-found.csv'))[-1] %>%
  rename(query = taxa)

smallphyla_notfound_tol <- read_csv(here(problems, 'not_found',
                                        '20220630_smallphyla_not_found-tol.csv')) 

smallphyla_conflicts <- full_join(smallphyla_notfound, smallphyla_family) %>%
  relocate(query) %>%
  full_join(smallphyla_notfound_tol)
```


```{r smallphyla-freshterr}
# list of freshwater/terrestrial genera
smallphyla_freshterr_gen <- smallphyla_freshterr %>%
  select(genus_split, freshwater_only, terrestrial_only) %>%
  distinct()

# filter for known fresh/terr genera
smallphyla_conflicts2 <- smallphyla_conflicts %>%
  filter(!(is.na(query))) %>%
  # extract genus names so we can test them
  separate(query, into = 'genus_split', " ", 1, 
           remove = FALSE, extra = 'drop') %>%
  select(!(c(is_marine, is_freshwater, is_brackish, is_terrestrial))) %>%
  left_join(smallphyla_freshterr_gen)

# merge generic level finds to original
smallphyla_freshterr2 <- smallphyla_conflicts2 %>%
  filter(!((freshwater_only %in% c(NA)) & (terrestrial_only %in% c(NA)))) %>%
  select(query, phylum, class, order, family, genus_split,
         freshwater_only, terrestrial_only) %>%
  rename(taxa_query = query) %>%
  full_join(smallphyla_freshterr)

# look at remaining
# start with order for smallphylas
smallphyla_conflicts_order <- smallphyla_conflicts %>%
  filter(!(query %in% smallphyla_freshterr2$taxa_query)) %>%
  select(order) %>%
  distinct()


# manually populate freshwater, terrestrial, and marine columns
smallphyla_conflicts_order <- smallphyla_conflicts_order %>%
  mutate(freshwater_only = ifelse(order %in% c(), '1', 
                                  ifelse(order %in% c('Cumacea','Opiliones'), '0', NA))) %>%
  mutate(terrestrial_only = ifelse(order %in% c('Opiliones'), '1', 
                                  ifelse(order %in% c('Cumacea'), '0', NA))) %>%
  mutate(is_marine = ifelse(order %in% c('Cumacea'), '1', 
                                  ifelse(order %in% c('Opiliones'), '0', NA)))


# filter conflicts again, merge with previous list
smallphyla_freshterr3 <- smallphyla_conflicts %>%
  filter(!(query %in% smallphyla_freshterr2$taxa_query)) %>%
  select(!(c(is_marine, is_freshwater, is_brackish, is_terrestrial))) %>%
  left_join(smallphyla_conflicts_order) %>%
  select(query, phylum, class, order, family,
         freshwater_only, terrestrial_only) %>%
  filter(freshwater_only == 1 | terrestrial_only == 1) %>%
  mutate(freshwater_only = as.numeric(freshwater_only)) %>%
  mutate(terrestrial_only = as.numeric(terrestrial_only)) %>%
  rename(taxa_query = query) %>%
  full_join(smallphyla_freshterr2)

write_csv(smallphyla_freshterr3, here(problems, 'fresh_terrestrial',
                                   '20220704_smallphyla_fresh-terr.csv'))
```

```{r}
smallphyla_conflicts4 <- smallphyla_conflicts %>%
  filter(!(query %in% smallphyla_freshterr3$taxa_query)) 

write_csv(smallphyla_conflicts4, here(problems, 'not_found',
                                   '20220704_smallphyla_not-found_outstanding.csv'))
```

